Identifying regime transitions for water governance at the Yellow River Basin, China

### 2023-10-07 paper/main/04_discussion.tex
docs(paper): :pencil2: delete the expression of lower stress in P1

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

>>>>

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
docs(paper): :pencil2: delete the expression of lower stress in P1

>>>>

% 1. 首先感谢指出这个表述问题，这确实造成了误解。
% 2. 其次，第一阶段确实出现了断流，但正如下图所展示的，断流的天数和长度都还偏小。第一阶段确实相对来说已经是压力比较小的，但增大的太过迅速。
% 3. 正如我们在新增的不同断点识别方法所诊断出的第一阶段结束在 1975-1978之间，而第一次出现断流的时间是1973年。就我们研究的时间尺度来说，已经是比较接近的识别了。但数据限制，没有办法非常完全准确到第一阶段没有断流。
% 4. 总的来说，第一阶段相对其他时期压力并不算大，但压力增速极大，导致第一阶段末出现断流现象。我们已经删除了容易歧义的表述。
\AR{} We extend our sincere gratitude for highlighting the inconsistency in our description. We acknowledge that our previous phrasing may have led to misunderstandings. We have taken the liberty to revise our manuscript, eliminating ambiguous phrases to ensure clarity and accuracy in paper.

\AR*{} We recognize that zero-flow events occurred during the first stage. However, both the duration and frequency of these events were relatively minor (worst in 1990s). While the water stress was indeed lower during this period, the rapid increase in stress levels was a significant concern.

\AR*{} With the introduction of additional breakpoint detection methods in our revised manuscript, we observed that the first stage ends between 1975 and 1978, aligning closely with the onset of zero-flow events in 1973. Given the temporal scale of our study and the limitations inherent in the available data, this alignment is reasonably accurate.

\AR*{} In summation, while the water stress during the first stage was not as pronounced as in subsequent periods, the accelerated rate of increase in stress levels culminated in zero-flow events towards the end of this stage.
